\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,xcolor}
\input{_macros}

\newtheorem{conjecture}{Conjecture}

\title{Stabilizing quantities $\rho_p$ for boundary control of PDE}
\author{Amaury Hayat}
\date{February 09, 2026}

\begin{document}
\maketitle

\section*{Context}

This is a question originally raised by Jean-Michel Coron in 2016.
When studying the stability of nonlinear PDE of the form
\begin{equation}
\partial_t u + A(u)\partial_x u + B(u) = 0, \quad \text{on } [0, L],
\end{equation}
where $u \in \mathbb{R}^n$ and with boundary conditions of the form
\begin{equation}
\begin{pmatrix} u_+(t, 0) \\ u_-(t, L) \end{pmatrix}
= G \begin{pmatrix} u_+(t, L) \\ u_-(t, 0) \end{pmatrix}
\end{equation}
a natural quantity that appears is the following function
\begin{equation}
\rho_p : M \mapsto \inf\{\|\Delta M \Delta^{-1}\|_p \mid \Delta = \mathrm{diag}(\delta_1, \ldots, \delta_n),\; \delta_i > 0,\; \forall\, i \in \{1, \ldots, n\}\},
\end{equation}
where $\|\cdot\|_p$ is the matrix $p$-norm.

\begin{conjecture}
For any $M \in \mathbb{R}^{n \times n}$ one has
\begin{equation}
\rho_2(M) \leq \rho_3(M) \leq \cdots \leq \rho_\infty(M).
\end{equation}
\end{conjecture}

A weaker version is:
\begin{conjecture}
For any $M \in \mathbb{R}^{n \times n}$ one has
\begin{equation}
\rho_2(M) \leq \rho_k(M), \quad \forall\, k \in \mathbb{N} \setminus \{0\}.
\end{equation}
\end{conjecture}

Another conjecture is:
\begin{conjecture}
For any $n > 6$, and any $p > 2$ ($n, p \in \mathbb{N}$) there exists $M \in \mathbb{R}^{n \times n}$ such that
\begin{equation}
\rho_p(M) < \rho_{p+1}(M).
\end{equation}
\end{conjecture}

\section*{What is already known}

The main previous works are in \cite{coron2008,coron2015}. In particular it is known that for any $n \in \mathbb{N}$ and any $M \in \mathbb{R}^{n \times n}$,
\begin{equation}
\rho_1(M) \geq \rho_2(M), \quad \rho_1(M) = \rho_\infty(M),
\end{equation}
and for $n \geq 2$ there exists $M \in \mathbb{R}^{n \times n}$ such that
\begin{equation}
\rho_1(M) > \rho_2(M).
\end{equation}
It is also known \cite{rump2003} that if $M$ has only non-negative coefficients then
\begin{equation}
\rho_k(M) = \rho_1(M), \quad \forall\, k \in [1, +\infty].
\end{equation}

\section*{Task: Prove Conjecture 3}

We aim to prove:

\medskip
\noindent\textbf{Conjecture 3.} \textit{For any $n > 6$, and any $p > 2$ ($n, p \in \mathbb{N}$) there exists $M \in \mathbb{R}^{n \times n}$ such that $\rho_p(M) < \rho_{p+1}(M)$.}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

\section*{Proof of Conjecture 3}

The proof proceeds in three steps. We first compute the induced $\ell_r$ operator norm of the $2\times 2$ Hadamard matrix, then show that diagonal scaling cannot reduce it, and finally observe that zero-padding preserves $\rho_r$. These combine to yield an explicit construction.

\input{section_1_hadamard_norm}
\input{section_2_scaling_invariance}
\input{section_3_zero_padding}

\subsection*{Step 4: Conclusion --- Proof of Conjecture 3}

\begin{theorem}\label{thm:conj3}
For any integers $n > 6$ and $p > 2$, there exists $M \in \mathbb{R}^{n \times n}$ such that $\rho_p(M) < \rho_{p+1}(M)$.
\end{theorem}

\begin{proof}
Let $H = \begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix}$ and define $M = H \oplus 0_{n-2} \in \mathbb{R}^{n \times n}$, where $0_{n-2}$ denotes the $(n-2)\times(n-2)$ zero matrix. Since $n > 6$, we have $n-2 \geq 5 \geq 0$, so the construction is valid.

By Lemma~\ref{lem:zero-padding} (with $B=H$, $m=2$, $k=n-2$),
\[
\rho_p(M) = \rho_p(H) \quad\text{and}\quad \rho_{p+1}(M) = \rho_{p+1}(H).
\]
By Lemma~\ref{lem:rho-hadamard}, since $p \geq 3 > 2$ and $p+1 \geq 4 > 2$,
\[
\rho_p(H) = 2^{1-1/p} \quad\text{and}\quad \rho_{p+1}(H) = 2^{1-1/(p+1)}.
\]
Since $p < p+1$, we have $\frac{1}{p} > \frac{1}{p+1}$, hence $1 - \frac{1}{p} < 1 - \frac{1}{p+1}$. Because the exponential function $\alpha \mapsto 2^\alpha$ is strictly increasing,
\[
\rho_p(M) = 2^{1-1/p} < 2^{1-1/(p+1)} = \rho_{p+1}(M).
\]
This completes the proof of Conjecture~3.
\end{proof}

\begin{thebibliography}{9}
\bibitem{coron2015} Jean-Michel Coron and Hoai-Minh Nguyen. \textit{Dissipative boundary conditions for nonlinear 1-D hyperbolic systems: sharp conditions through an approach via time-delay systems.} SIAM J.\ Math.\ Anal., 47(3):2220--2240, 2015.

\bibitem{coron2008} Jean-Michel Coron, Georges Bastin, and Brigitte d'Andr\'ea-Novel. \textit{Dissipative boundary conditions for one-dimensional nonlinear hyperbolic systems.} SIAM Journal on Control and Optimization, 47(3):1460--1498, 2008.

\bibitem{rump2003} Siegfried M.\ Rump. \textit{Optimal scaling for $p$-norms and componentwise distance to singularity.} IMA Journal of Numerical Analysis, 23(1):1--9, 2003.
\end{thebibliography}

\end{document}
