\[
\textbf{Proof.}
\]
For clarity, write \(H_m\) for the Sylvester--Hadamard matrix of order \(m=2^k\). Thus \(H_1=(1)\), and for \(m=2n\),

\[
H_m
=
H_{2n}
=
\begin{pmatrix}
H_n & H_n\\
H_n & -H_n
\end{pmatrix}.
\]

We prove the stated properties.

---

### (a) \(H\) is symmetric and has only \(\pm 1\) entries

We prove by induction on \(k\) that \(H_{2^k}\) is symmetric and every entry of \(H_{2^k}\) is equal to \(+1\) or \(-1\).

For \(k=0\), we have \(H_1=(1)\), which is symmetric and has only \(+1\) entries.

Assume now that \(H_n\) is symmetric and has only \(\pm 1\) entries. Consider

\[
H_{2n}
=
\begin{pmatrix}
H_n & H_n\\
H_n & -H_n
\end{pmatrix}.
\]

Every block \(H_n\) and \(-H_n\) has only \(\pm 1\) entries, so \(H_{2n}\) also has only \(\pm 1\) entries. Moreover, since \(H_n^\top=H_n\), we have

\[
H_{2n}^\top
=
\begin{pmatrix}
H_n^\top & H_n^\top\\
H_n^\top & (-H_n)^\top
\end{pmatrix}
=
\begin{pmatrix}
H_n & H_n\\
H_n & -H_n
\end{pmatrix}
=
H_{2n}.
\]

Thus \(H_{2n}\) is symmetric. By induction, \(H_m\) is symmetric and has only \(\pm 1\) entries for every \(m=2^k\).

---

### (b) \(H^\top H=H^2=mI_m\)

Since \(H_m\) is symmetric by part (a), it suffices to prove

\[
H_m^2=mI_m.
\]

We prove this by induction on \(m=2^k\).

For \(m=1\),

\[
H_1^2=(1)^2=(1)=I_1.
\]

So the claim holds for \(m=1\).

Assume now that for some \(n=2^{k-1}\), we have

\[
H_n^2=nI_n.
\]

Let \(m=2n\). Then

\[
H_{2n}
=
\begin{pmatrix}
H_n & H_n\\
H_n & -H_n
\end{pmatrix}.
\]

Multiplying block matrices gives

\[
H_{2n}^2
=
\begin{pmatrix}
H_n & H_n\\
H_n & -H_n
\end{pmatrix}
\begin{pmatrix}
H_n & H_n\\
H_n & -H_n
\end{pmatrix}.
\]

Therefore

\[
H_{2n}^2
=
\begin{pmatrix}
H_n^2+H_n^2 & H_n^2-H_n^2\\
H_n^2-H_n^2 & H_n^2+H_n^2
\end{pmatrix}
=
\begin{pmatrix}
2H_n^2 & 0\\
0 & 2H_n^2
\end{pmatrix}.
\]

Using the induction hypothesis \(H_n^2=nI_n\), we get

\[
H_{2n}^2
=
\begin{pmatrix}
2nI_n & 0\\
0 & 2nI_n
\end{pmatrix}
=
2nI_{2n}.
\]

Since \(m=2n\), this is exactly

\[
H_m^2=mI_m.
\]

Thus, by induction,

\[
H^2=mI_m.
\]

Finally, since \(H^\top=H\), we have

\[
H^\top H=H^2=mI_m.
\]

---

### (c) Operator norms of \(H\)

We compute the three stated operator norms.

#### Spectral norm

The spectral norm satisfies

\[
\|H\|_{2\to 2}^2
=
\lambda_{\max}(H^\top H),
\]

where \(\lambda_{\max}(H^\top H)\) denotes the largest eigenvalue of the positive semidefinite matrix \(H^\top H\).

From part (b),

\[
H^\top H=mI_m.
\]

Every eigenvalue of \(mI_m\) is equal to \(m\). Hence

\[
\|H\|_{2\to 2}^2=m,
\]

and therefore

\[
\|H\|_{2\to 2}=\sqrt{m}.
\]

#### \(\ell^1\) operator norm

For a matrix \(A=(a_{ij})\), its induced \(\ell^1\) operator norm is

\[
\|A\|_{1\to 1}
=
\max_{1\leq j\leq m}\sum_{i=1}^m |a_{ij}|,
\]

the maximum absolute column sum.

Since every entry of \(H\) is either \(+1\) or \(-1\), we have

\[
|H_{ij}|=1
\]

for every \(i,j\). Therefore each column has absolute column sum

\[
\sum_{i=1}^m |H_{ij}|
=
\sum_{i=1}^m 1
=
m.
\]

Hence

\[
\|H\|_{1\to 1}=m.
\]

#### \(\ell^\infty\) operator norm

For a matrix \(A=(a_{ij})\), its induced \(\ell^\infty\) operator norm is

\[
\|A\|_{\infty\to \infty}
=
\max_{1\leq i\leq m}\sum_{j=1}^m |a_{ij}|,
\]

the maximum absolute row sum.

Again, since \(|H_{ij}|=1\) for all \(i,j\), each row has absolute row sum

\[
\sum_{j=1}^m |H_{ij}|
=
\sum_{j=1}^m 1
=
m.
\]

Thus

\[
\|H\|_{\infty\to \infty}=m.
\]

Therefore,

\[
\boxed{
\|H\|_{2\to 2}=\sqrt{m},
\qquad
\|H\|_{1\to 1}=m,
\qquad
\|H\|_{\infty\to \infty}=m.
}
\]

---

### (d) \(Hh_i=me_i\)

Let \(h_i\) be the \(i\)th row of \(H\), viewed as a column vector. By definition,

\[
h_i
=
\begin{pmatrix}
H_{i1}\\
H_{i2}\\
\vdots\\
H_{im}
\end{pmatrix}.
\]

This is the \(i\)th column of \(H^\top\), so

\[
h_i=H^\top e_i.
\]

Since \(H\) is symmetric, \(H^\top=H\), hence

\[
h_i=He_i.
\]

Using part (b), we get

\[
Hh_i
=
H(He_i)
=
H^2e_i
=
mI_me_i
=
me_i.
\]

Therefore, for every \(i\in\{1,\ldots,m\}\),

\[
\boxed{Hh_i=me_i.}
\]

This completes the proof.